\documentclass[letterpaper, 17pt]{article}
\usepackage{extsizes}
\usepackage[margin=1.0in]{geometry}
\usepackage{xlop}
\usepackage{amsmath,tabu}

\newcommand{\white}[1]{}

% CS	---	Compound Sentence
% IL	---	Item List
% C	---	Capitalization
% EP	---	Ending Punctuation
% SO	---	So
% DC	---	Dependent Clause
% EX	---	Extraneous Punctuation
% WH	---	Which Or That
% RS	---	Run-on Sentence

\begin{document}

\section*{General Grammar}

\begin{itemize}
	\item He went to the mall but she went to the park.	% CS

	\item the garden was overgrown with wildflowers and weeds creating a beautiful mess.	% C, DC

	\item The laughter of children playing in the park was infectious making me smile	% DC, EP

	\item the sun was shining brightly in the sky but the air was chilly with a hint of autumn	% C, CS, EP

	\item She loved to read books but she also loved to write her own stories and poems.	% CS

	\item My sister is an artist, so she spends most of her time painting drawing and sculpting	% EP, IL, SO

	\item do you think that we need to buy another cake.	% C, EP

	\item After I eat cake I brush my teeth so that I don't get, a cavity.	% DC, SO, EX

	\item The storm was approaching fast so we closed all the windows and locked the doors	% SO, EP

	\item The dog barked loudly which made me think of cake	% WH, EP

	\item i love to travel to new places and try new foods but i always miss home after a few days.	% C, CS

	\item soon the store will be closed stopping us from buying more cake	% C, DC, EP

	\item A tall man walked into the room and his name was mr cake.	% CS, C
\end{itemize}

\newpage
\section*{Run-on Sentences}

\begin{itemize}
	\item The sun was shining brightly and the birds were chirping in the trees and people were strolling leisurely in the park it was a beautiful day indeed.	% RS

	\item I woke up early this morning I brushed my teeth I took a shower I made breakfast I drank coffee I read the news I walked my dog I went to work I arrived late I apologized to my boss I sat at my desk I answered emails I attended a meeting I had lunch with my colleagues I worked on a project I made phone calls I attended another meeting I went home I cooked dinner I watched TV I went to bed exhausted.	% RS

	\item The sun was shining brightly in the clear blue sky it was a beautiful day for a picnic with friends and family everyone gathered at the park grilling hot dogs and hamburgers playing games and enjoying each other's company.	% RS

	\item She was laughing uncontrollably with tears streaming down her face her friends couldn't help but join in the laughter as they reminisced about all the silly moments they had shared over the years.	% RS

	\item The storm clouds rolled in quickly thunder boomed and lightning flashed people ran for cover seeking refuge under awnings and trees cars splashed through puddles and umbrellas turned inside out it was a chaotic scene of nature's power and human resilience.	% RS

	\item Yesterday, I went to the beach with my friends we swam in the ocean, built sandcastles, and had a picnic under the sunny blue sky we even played volleyball until the sun started to set it was a perfect day.	% RS

	\item The sun was shining brightly in the cloudless sky it cast a warm golden hue on the fields and meadows, the birds were chirping happily as they flitted from tree to tree, the flowers danced in the gentle breeze, it was a perfect day.	% RS
\end{itemize}

\newpage
\section*{Dependent Clauses and General Grammar}

\begin{itemize}
	\item Although it was raining outside the children decided to play soccer in the muddy field	% DC, EP

	\item With great anticipation the young chess champion took a deep breath and made his final move winning the game.	% DC

	\item Running at top speed George quickly made it to the great pink house.	% DC

	\item after finishing her homework Sarah went to the library to borrow some books for her science project.	% DC, C

	\item As the teacher discussed fractions little Susie's mind wandered off to thoughts of pizza imagining herself happily dividing a pizza into equal slices for all her friends	% EP, DC

	\item The brave firefighters quickly ran towards the burning building risking their lives to save trapped people and extinguish the flames		% DC, EP

	\item after building a big sandcastle the boy decided to destroy it by pouring a bucket of water on top.	% DC, C

	\item Although she had never ridden a bike before Emily managed to pedal without training wheels on her First try.	% DC, C

	\item While George finished his homework his hungry hamster cheered him on	% DC, EP
\end{itemize}

\newpage
\section*{Run-on Sentences}

\begin{itemize}
	\item My dog loves to run in the park he jumps and barks and chases his tail whenever we go outside.	% RS
	
	\item Bob is my best friend he always makes me laugh with his silly jokes he's really funny.	% RS

	\item The sun is shining brightly in the sky it makes everything feel warm and happy and I can't wait to go swimming later.	% RS

	\item My mom is an amazing cook she makes the most delicious meals she makes spaghetti and meatballs on Mondays and she just makes meatballs on Tuesdays and she makes us a big bowl of spaghetti sauce on Wednesdays.	% RS

	\item I went to the store to buy some groceries but I forgot my wallet so I had to go back home and get it and by the time I returned to the store, it was already closed for the day.	% RS

	\item Jimmy went to the store to buy soap when he got there he decided to buy eggs too so he bought a dozen of them.	% SO, RS

	\item The children were playing in the park and laughing joyfully and running around with their friends and it was a delightful sight to see their happiness.	% RS

	\item There lived a man named Mr. Bumblebee he wore mismatched socks and talked to his pet rock named Fred he had a passion for collecting rubber ducks that he displayed in his bathtub.	% RS
\end{itemize}

\newpage
\section*{Simple Use Of ``So''}

If ``so that'' fits, then you don't need a comma.

\begin{itemize}
	\item I went to the store so I could buy bread.	% SO
	\item I needed bread so I went to the store.	% SO
	\item The glue was weak so the glass broke.	% SO
	\item I cut down trees so he could build a house.	% SO
	\item The car was gone so we knew that my uncle had left.	% SO
	\item We need eggs so go get some.	% SO
	\item You should plug the toaster in so you can make toast.	% SO
	\item We read the bible so we can understand it.	% SO
	\item The wall did not break so the house did not fall.	% SO
	\item The athlete became tired so she fell down.	% SO
	\item She made breakfast so you don't have to.	% SO
	\item We are doing well so I think that we will win.	% SO
	\item Everyone opened their eyes so they could see.	% SO
	\item We arrive so the children stopped saying "are we there yet?"	% SO
	\item You eat broccoli so you will be strong.	% SO
\end{itemize}

\newpage
\section*{Use Of ``So''}

\begin{itemize}
	\item He missed his flight so he had to book another one for the next day.	% SO
	\item The concert was so loud that my ears were ringing.	% SO
	\item I was hungry so I ordered a pizza for dinner.	% SO
	\item He took a break from work so he could think.	% SO
	\item The movie was sold out so we had to choose another one to watch.	% SO
	\item I cleaned the house so I could impress my guests.	% SO
	\item The storm was so strong that it knocked down trees.	% SO
	\item He bought a new car so he could commute to work more efficiently.	% SO
	\item The pizza was so hot that it burned her.	% SO
	\item The book is so good that I couldn't put it down.	% SO
	\item The weather was nice so we decided to have a picnic in the park.	% SO
	\item The mountain was so high that it took hours to climb.	% SO
	\item The store was closed so we had to find another place to buy groceries.	% SO
	\item She applied for the job so she could gain more experience.	% SO
	\item She was so excited that she couldn't sit still.	% SO
\end{itemize}

\newpage
\section*{Use Of ``So''}

\begin{itemize}
	\item The movie was so scary that I had to cover my eyes.	% SO
	\item I forgot my keys so I had to wait for my roommate to get home.	% SO
	\item They saved up their money so they could afford to go on vacation.	% SO
	\item The water was so cold that I shivered from head to toe.	% SO
	\item I decided to start exercising so I could improve my health.	% SO
	\item I woke up early so I could finish my work before the deadline.	% SO
	\item The party was so fun that I didn't want it to end.	% SO
	\item I finished my work early so I decided to take a break.	% SO
	\item We set up a meeting so we could discuss the project.	% SO
	\item She studied hard so she could pass her exams.	% SO
	\item The dog was so cute that I couldn't resist petting it.	% SO
	\item She was feeling sick so she stayed home from school.	% SO
	\item I woke up late so I rushed to get ready for work.	% SO
	\item I was tired so I went to bed early.	% SO
	\item He bought a new bike so he could go to the store faster.	% SO
	\item The chicken was so hot that it burned him.	% SO
	\item The movie was so exciting that we couldn't stop watching it.	% SO
\end{itemize}

\newpage
\section*{Run-on Sentences}

\begin{itemize}
	\item I woke up early this morning it was still dark outside I got dressed quickly and left the house without having breakfast I had to catch the first bus to go to work.	% RO
	\item She went to the store to buy some groceries she bought some eggs milk bread cheese and vegetables she paid for everything with her credit card she put the groceries in her car and drove back home.	% RO IL
	\item The FedEx driver delivered five packages to the wrong house then he wasted the rest of the day playing hopscotch finally he hid the rest of the mail in a cave and went home.	% RO
	\item They decided to go on a road trip they packed their bags and left early in the morning they drove for hours without taking any breaks they stopped at a gas station to fill up the tank and buy some snacks.	% RO
	\item Yesterday, I spent the whole day playing games I woke up early in the morning and started playing and didn't stop until late at night my eyes were tired and red and I had to go to sleep.	% RO
	\item I sat down at my laptop to write some sentences I am very careful when I write sentences I make sure that none of the sentences are about cake cake should never be mentioned in any sentence.	% RO
\end{itemize}

\newpage
\section*{Run-on Sentences}

\begin{itemize}
	\item When I was a kid, I used to play games all the time I loved playing outside with my friends and we would play games like tag and hide-and-seek sometimes we would play inside and we would play games like Candy Land and Chutes and Ladders.	% RO
	\item He studied for his exam for hours and he read all the textbooks and he took notes and he practiced problems and he asked his classmates for help and he went to the library and he borrowed some books and he stayed up late and he drank coffee and he felt nervous and he hoped he would do well.	% RO
	\item Doughnuts are my absolute favorite food in the whole entire world they're just so sweet and sugary and delicious and I could eat them every single day for breakfast and lunch and dinner and never get tired of them at all.	% RO
	\item I think that doughnuts are a really important part of our culture and our society and they bring people together in a way that no other food can because everyone loves doughnuts and everyone can find something to enjoy about them.	% RO
	\item Bracelets come in all shapes and sizes they can be made of metal, leather, beads, or fabric, some bracelets are simple and elegant while others are bold and colorful, people wear bracelets for different reasons.	% RO
	\item Welcome to the doughnut parade everyone is welcome here come the giant doughnut cart and the doughnut clowns.	% RO
\end{itemize}
\end{document}
